What's in a Domain? Anaylsis of URL Features

### 2022-10-09 paper/paper.tex
updating feature importance plot to include param fragment

\begin{figure*}
\centering
\includegraphics[scale=0.3]{images/URL_parts.png}
\caption{Structural components of a URL requiring specific feature engineering treatment}
\label{fig:url_structure}
\end{figure*}

@@

@@

              &domain\_reg\_year      &Numeric     &Year in which the domain was initially registered    \\

@@

@@

@@

@@

The data used in this study was colated from a range of publications that 
present internet classification problems containing URLs as the primary feature.
The ISCX Malcious URL classification dataset contains both malware and phishing URLS 
that need to be discriminated against benign URLS\cite{Mamun2016}.
The world wide web knowledge base (WebKb) 4 Universities data set contains a wide
range of university URLs categorised into multiple topic categories\cite{Craven1998}.
The Syskill \& Webert webpage ratings dataset containing webepages across 4 categories
with a human generated categorisation for determining personal preferences in webpage
content\cite{Pazzani1996}. These 4 URL classification problems are summarised in Table \ref{tab:data}

\begin{table}
\caption{Datasets}
\label{tab:data}
\begin{tabular}{|l|r|r|r|}
\toprule
Dataset              &Records        &Classes  &Majority    \\
\midrule
Malware              &46,944          &2       &75\%        \\
Phishing             &45,343          &2       &78\%        \\
WebKb 4Uni           &8,284           &7       &45\%        \\
Syskill \& Webert    &330             &3       &68\%        \\
DMOZ                 &1,562,978       &15      &16\%        \\
\bottomrule
\end{tabular}
\end{table}

We generate all url features for each of these datasets and then apply a range of machine learning
techniques to build classifiers that can be analysed for key features for each task.

@@

A set of standard machine learning pipelines are applied to each of the four problems. Each approach is applied
using default parameters, without any fine tuning. We use feature preprocessing modules appropriate for each class
of model. All details are available in the source repository for the experiments. The performance of the models
is tabulated in Table \ref{tab:results}, where we show Balanced Accuracy of each model on the holdout data, as this
metric is appropriate and comparable across all four problems.

\begin{table}
\caption{Machine Learning Results}
\label{tab:results}
\begin{tabular}{|l|r|r|r|r|}
\toprule
Dataset              &NB     &LR    &XT    &LGBM     \\
\midrule
Malware              &0.65   &0.93  &0.99  &1.00     \\
Phishing             &0.89   &0.98  &0.99  &1.00     \\
WebKb 4Uni           &0.30   &0.36  &0.58  &0.49     \\
Syskill \& Webert    &0.39   &0.35  &0.37  &0.33     \\
DMOZ                 &0.12   &0.17  &0.29  &0.25     \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{figure*}
\centering
\includegraphics[scale=0.6]{images/URL_parts.png}
\caption{Structural components of a URL requiring specific feature engineering treatment}
\label{fig:url_structure}
\end{figure*}

@@

              &domain\_len            &Numeric     &Character length of the domain name (minus TLD and subdomain)     \\
              &domain\_alpha          &Numeric     &Proportion of characters in the domain that are letters    \\

@@

              &subdomain              &Category    &The text value of the subdomain  \\

@@

              &keys\_count            &Numeric     &Count of the distinct keys used in the parameter string  \\

@@

              &values\_count          &Numeric     &Count of the distinct values used in the parameter string  \\

@@

              &frag\_len              &Numeric     &The character length of the fragment string    \\
              &frag\_secs             &Numeric     &Count of distinct sections in the fragment string delimited by [?\&=]  \\
              &frag\_enc\_char        &Boolean     &Flag indicating presence of an encoded character within the fragment string    \\

@@

The data used in this study was colated from a range of sources to represent a varity of 
Internet resource classification problems containing URLs as the primary feature.
The ISCX Malcious URL classification dataset contains malware, spam and phishing URLS 
that need to be discriminated against a set of benign URLS\cite{Mamun2016}.
The world wide web knowledge base (WebKb) 4 Universities data set contains a wide
range of university URLs categorised into multiple topic categories\cite{Craven1998}.
The Syskill \& Webert webpage ratings dataset containing webepages across 4 categories
with a human generated categorisation for determining personal preferences in webpage
content\cite{Pazzani1996}. Finally, we utilise the Kaggle DMOZ dataset that contains 
a large set of topic categorised URLs\cite{dmoz}.

These 6 URL classification problems are summarised in Table \ref{tab:data}, where
show the number of records, the cardinality of the target classes, and the proportion
of the data that belongs to the most common class in the set.

\begin{table}
\caption{Datasets}
\label{tab:data}
\begin{tabular}{|l|r|r|r|}
\toprule
Dataset              &Records        &Classes  &Majority    \\
\midrule
spam                 &47,378          &2       &75\%        \\
Malware              &46,944          &2       &75\%        \\
Phishing             &45,343          &2       &78\%        \\
WebKb 4Uni           &8,284           &7       &45\%        \\
Syskill \& Webert    &330             &3       &68\%        \\
DMOZ                 &1,562,978       &15      &16\%        \\
\bottomrule
\end{tabular}
\end{table}

We generate all URL features for each of these datasets and then apply a range of machine learning
techniques to build classifiers that can be analysed for key features for each task.

@@

A set of standard machine learning pipelines are applied to each of the four problems. Each approach is applied
using default parameters, without any fine tuning. We use feature preprocessing modules appropriate for each class
of model. All details are available in the source repository for the experiments. The performance of the models
is tabulated in Table \ref{tab:results}, where we show Balanced Accuracy of each model on the holdout data, as this
metric is appropriate and comparable across all six problems.

\begin{table}
\caption{Machine Learning Results}
\label{tab:results}
\begin{tabular}{|l|r|r|r|r|}
\toprule
Dataset              &NB     &LR    &XT    &LGBM     \\
\midrule
Spam                 &1.00   &1.00  &1.00  &1.00     \\
Malware              &0.65   &0.93  &0.99  &1.00     \\
Phishing             &0.89   &0.98  &0.99  &1.00     \\
WebKb 4Uni           &0.30   &0.36  &0.58  &0.49     \\
Syskill \& Webert    &0.39   &0.35  &0.37  &0.33     \\
DMOZ                 &0.12   &0.17  &0.29  &0.25     \\
\bottomrule
\end{tabular}
\end{table}

It should be clear from this table that the internet security probelms are much more amenable to URL based 
classification. All three of these problems result in high performing classifiers. In comparison the topic
and user preference based tasks achieve far more modest performance. These problems are hindered by both higher 
cardinality targets, and 2 or the 3 data sets being much smaller. However, the results suggest that in general
URL based topic classification is likely to be difficult.
